### 2011-04-03 docs/enthalpy/enthalpy.tex
some small fixes and a comment on why h

The full enthalpy equation, with no approximations, appears as:
\begin{equation}
\frac{\partial(\rho h)}{\partial t} = -\nabla\cdot(\rho h\Ub) + 
  \frac{Dp}{Dt} + \rho\Hnuc \label{eq:enthalpy}
\end{equation}
Here, $h = e + p/\rho$ is the specific enthalpy, with $e$ the specific
internal energy.  In the low Mach number formulation, we replace $p$
with $p_0$ in the $Dp/Dt$ term, however, the definition of enthalpy
implicitly contains a pressure.  When calling the equation of state,
we take $h$ and $\rho$ as inputs.  The equation of state is expressed
in terms of $T$ and $\rho$, so it iterates until it finds the $h$ that
we desire.  This $h$ will be of the form $h = e + p_\mathrm{EOS}/rho$,
where $p_\mathrm{EOS}$ is the pressure returned from the EOS.  Note that
$p_\mathrm{EOS}$ may not be equal to $p_0$---this causes us to drive
off of the constraint. \MarginPar{not completely sure what to say here}

@@

\begin{itemize}
\item Why do we want to start with enthalpy instead of internal energy?

@@

\item In the EOS, we take $h$ and construct $e$ by subtracting off
  $p$---depending on the inputs to the EOS, we treat the '$p$' part of $h$
  differently.

@@

\item do we want to always insist that the '$p$' hidden in the definition of
   $h$ is $p_0$?

\end{itemize}

>>>>

The full enthalpy equation, with no approximations, appears as:
\begin{equation}
\frac{\partial(\rho h)}{\partial t} = -\nabla\cdot(\rho h\Ub) + 
  \frac{Dp}{Dt} + \rho\Hnuc \label{eq:enthalpy}
\end{equation}
Here, $h = e + p/\rho$ is the specific enthalpy, with $e$ the specific
internal energy.  In the low Mach number formulation, we replace $p$
with $p_0$ in the $Dp/Dt$ term, however, the definition of enthalpy
implicitly contains a pressure.  When calling the equation of state,
we take $h$ and $\rho$ as inputs.  The equation of state is expressed
in terms of $T$ and $\rho$, so it iterates until it finds the $h$ that
we desire.  This $h$ will be of the form $h = e + p_\mathrm{EOS}/\rho$,
where $p_\mathrm{EOS}$ is the pressure returned from the EOS.  Note that
$p_\mathrm{EOS}$ may not be equal to $p_0$---this causes us to drive
off of the constraint. \MarginPar{not completely sure what to say here}

@@

\begin{enumerate}
\item Why do we want to start with enthalpy instead of internal energy?

   We believe that the original desire stems from our experience with smallscale 
   combustion.  There, stratification is not important and $Dp_0/Dt = 0$, so
   the enthalpy equation becomes a conservation equation for $(\rho h)$.

@@

\item In the EOS, we take $h$ and construct $e$ by subtracting off
  $p$---depending on the inputs to the EOS, we treat the `$p$' part of $h$
  differently.

@@

\item do we want to always insist that the `$p$' hidden in the definition of
   $h$ is $p_0$?

\end{enumerate}
